### 2019-01-05 methods.tex
explicit tabularnewlines
weird sentence about pa233 fixed

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[h!]
        %\centering
        \caption{Summary of principal data for \gls{MSBR} 
        \cite{robertson_conceptual_1971}.}
        \begin{tabularx}{\textwidth}{ s  s}
        \hline
                Thermal capacity of reactor           		& 2250 MW(t)
                \\ Net electrical output                 		& 1000 
        MW(e) \\  Net thermal efficiency        				
        & 44.4\%
                \\  Salt volume fraction in central zone I		& 0.13
                \\ Salt volume fraction in outer zone II       & 0.37
                \\ Fuel salt inventory (Zone I)                & 8.2 m$^3$	
        \\ Fuel salt inventory (Zone II)               & 10.8 m$^3$	\\ Fuel 
        salt inventory (annulus)               & 3.8 m$^3$	\\  Total fuel 
        salt inventory                   & 48.7 m$^3$	\\ Fissile mass in fuel 
        salt                   & 1303.7 kg	\\ Fuel salt components                  
                               & LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$	\\  
        Fuel salt composition                 & 71.75-16-12-0.25 mole\%
                \\
                Fuel salt density                    & 3.35 g/cm$^3$
                \\ \hline
        \end{tabularx}
        \label{tab:msbr_tab}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsubsection{Fuel material flows}
The $^{232}$Th in the fuel absorbs thermal neutrons and produces $^{233}$Pa 
which then decays into the fissile $^{233}$U. Furthermore, the \gls{MSBR} 
design requires online reprocessing to remove all poisons (e.g. $^{135}$Xe), 
noble metals, and gases (e.g. $^{75}$Se, $^{85}$Kr) every 20 seconds. 
Protactinium presents a challenge, since it has a large absorption cross 
section in the thermal energy spectrum. Moreover, $^{233}$Pa left in the core
 would produce $^{234}$Pa and $^{234}$U, neither of which are useful as fuel, 
 would produce a smaller amount of $^{233}$Pa which decays into the fissile $^{233}$U.
Accordingly, $^{233}$Pa is continuously 
removed from the fuel salt into a protactinium decay tank to allow $^{233}$Pa 
to decay to $^{233}$U without the corresponding negative neutronic impact. The reactor 
reprocessing system must separate $^{233}$Pa from the molten-salt fuel over 3 
days, hold it while $^{233}$Pa decays into $^{233}$U, and return it back to the 
primary loop. This feature allows the reactor to avoid neutron losses to 
protactinium, lowers in-core fission product inventory, and increases the 
efficiency of $^{233}$U breeding. Table~\ref{tab:reprocessing_list} summarizes 
full list of nuclides and the ``cycle times''\footnote{ The \gls{MSBR} program defined a ``cycle time" as the amount of time required to remove 100\% of a target nuclide from a fuel 
salt \cite{robertson_conceptual_1971}.} used for modeling salt treatment and 
separations \cite{robertson_conceptual_1971}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[ht!]
        \centering
        \caption{The effective cycle times for protactinium and fission 
        products removal (reproduced from \cite{robertson_conceptual_1971}).}
        \begin{tabularx}{\textwidth}{ x | s | x }
        \hline Processing group & \qquad\qquad\qquad Nuclides & Cycle time (at 
                full power) \\ \hline Rare earths & Y, La, Ce, Pr, Nd, Pm, Sm, 
                Gd & 50 days \\ \qquad & Eu & 500 days \\ Noble metals & Se, 
                Nb, Mo, Tc, Ru, Rh, Pd, Ag, Sb, Te & 20 sec \\
        Seminoble metals & Zr, Cd, In, Sn & 200 days \\
        Gases & Kr, Xe & 20 sec \\ Volatile fluorides & Br, I & 60 days \\
        Discard & Rb, Sr, Cs, Ba & 3435 days \\ 
        %Salt discard & Th, Li, Be, F & 3435 days \\ 
        Protactinium & $^{233}$Pa & 3 days \\ Higher 
                nuclides & $^{237}$Np, $^{242}$Pu & 16 years \\  \hline
        \end{tabularx}
        \label{tab:reprocessing_list}
\end{table}
The removal rates vary among nuclides in this reactor concept which dictate the 
necessary resolution of depletion calculations. If the depletion time intervals 
are very short, an enormous number of depletion steps are required to obtain 
the equilibrium composition. On the other hand, if the depletion  calculation 
time interval is too long, the impact of short-lived fission products is not 
captured. To compromise, a 3 day time interval was selected for depletion 
calculations\footnote{ Optimal depletion time step of 3 days for \gls{MSR} 
batch-wise depletion simulation was first described and concluded by Powers 
\emph{et al.} \cite{powers_new_2013}.} to correlate with the removal interval 
of 
$^{233}$Pa and $^{232}$Th was continuously added to maintain the initial mass 
fraction of $^{232}$Th.

@@

This approach works well for fast-removing elements (gases, noble metals, 
protactinium) which should be removed each depletion step. Unfortunately, 
for the elements with longer cycle times (i.e. rare earths should be removed 
every 50 days) this simplified approach leads to oscillatory behavior of all
major parameters. In future releases of SaltProc, this drawback will be eliminated 
by removing elements with longer cycle times using different method: only mass 
fraction (calculated separately for each reprocessing group) will be removed each
 depletion step or batch (e.g. in the current work it was chosen 3 days).

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[h!]
        \caption{Summary of principal data for \gls{MSBR} 
        \cite{robertson_conceptual_1971}.}
        \begin{tabularx}{\textwidth}{ s  s}
        \hline
                Thermal capacity of reactor           		& 2250 MW(t)
                \\ Net electrical output                 		& 1000 
        MW(e) \\  Net thermal efficiency        				
        & 44.4\%
                \\  Salt volume fraction in central zone I		& 0.13
                \\ Salt volume fraction in outer zone II       & 0.37
                \\ Fuel salt inventory (Zone I)                & 8.2 m$^3$	
        \\ Fuel salt inventory (Zone II)               & 10.8 m$^3$	\\ Fuel 
        salt inventory (annulus)               & 3.8 m$^3$	\\  Total fuel 
        salt inventory                   & 48.7 m$^3$	\\ Fissile mass in fuel 
        salt                   & 1303.7 kg	\\ Fuel salt components                  
                               & LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$	\\  
        Fuel salt composition                 & 71.75-16-12-0.25 mole\%
                \\
                Fuel salt density                    & 3.35 g/cm$^3$
                \\ \hline
        \end{tabularx}
        \label{tab:msbr_tab}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsubsection{Fuel material flows}
The $^{232}$Th in the fuel absorbs thermal neutrons and produces $^{233}$Pa 
which then decays into the fissile $^{233}$U. Furthermore, the \gls{MSBR} 
design requires online reprocessing to remove all poisons (e.g. $^{135}$Xe), 
noble metals, and gases (e.g. $^{75}$Se, $^{85}$Kr) every 20 seconds. 
Protactinium presents a challenge, since it has a large absorption cross 
section in the thermal energy spectrum. Moreover, $^{233}$Pa left in the core
would produce $^{234}$Pa and $^{234}$U, neither of which are useful as fuel. 
Accordingly, $^{233}$Pa is continuously 
removed from the fuel salt into a protactinium decay tank to allow $^{233}$Pa 
to decay to $^{233}$U without the corresponding negative neutronic impact. The reactor 
reprocessing system must separate $^{233}$Pa from the molten-salt fuel over 3 
days, hold it while $^{233}$Pa decays into $^{233}$U, and return it back to the 
primary loop. This feature allows the reactor to avoid neutron losses to 
protactinium, lowers in-core fission product inventory, and increases the 
efficiency of $^{233}$U breeding. Table~\ref{tab:reprocessing_list} summarizes 
full list of nuclides and the ``cycle times''\footnote{ The \gls{MSBR} program defined a ``cycle time" as the amount of time required to remove 100\% of a target nuclide from a fuel 
salt \cite{robertson_conceptual_1971}.} used for modeling salt treatment and 
separations \cite{robertson_conceptual_1971}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[ht!]
        \caption{The effective cycle times for protactinium and fission 
        products removal (reproduced from \cite{robertson_conceptual_1971}).}
        \begin{tabularx}{\textwidth}{ x | s | x }
        \hline Processing group & \qquad\qquad\qquad Nuclides & Cycle time (at 
                full power) \\ \hline Rare earths & Y, La, Ce, Pr, Nd, Pm, Sm, 
                Gd & 50 days \\ \qquad & Eu & 500 days \\ Noble metals & Se, 
                Nb, Mo, Tc, Ru, Rh, Pd, Ag, Sb, Te & 20 sec \\
        Seminoble metals & Zr, Cd, In, Sn & 200 days \\
        Gases & Kr, Xe & 20 sec \\ Volatile fluorides & Br, I & 60 days \\
        Discard & Rb, Sr, Cs, Ba & 3435 days \\ 
        %Salt discard & Th, Li, Be, F & 3435 days \\ 
        Protactinium & $^{233}$Pa & 3 days \\ Higher 
                nuclides & $^{237}$Np, $^{242}$Pu & 16 years \\  \hline
        \end{tabularx}
        \label{tab:reprocessing_list}
\end{table}
The removal rates vary among nuclides in this reactor concept which dictate the 
necessary resolution of depletion calculations. If the depletion time intervals 
are very short, an enormous number of depletion steps are required to obtain 
the equilibrium composition. On the other hand, if the depletion  calculation 
time interval is too long, the impact of short-lived fission products is not 
captured. To compromise, a 3 day time interval was selected for depletion 
calculations\footnote{ Optimal depletion time step of 3 days for \gls{MSR} 
batch-wise depletion simulation was first described and concluded by Powers 
\emph{et al.} \cite{powers_new_2013}.} to correlate with the removal interval 
of 
$^{233}$Pa and $^{232}$Th was continuously added to maintain the initial mass 
fraction of $^{232}$Th.

@@

This approach works well for fast-removing elements (gases, noble metals, 
protactinium) which should be removed each depletion step. Unfortunately, 
for the elements with longer cycle times (i.e. rare earths should be removed 
every 50 days) this simplified approach leads to oscillatory behavior of all
major parameters. In future releases of SaltProc, this drawback will be eliminated 
by removing elements with longer cycle times using different method: only mass 
fraction (calculated separately for each reprocessing group) will be removed each
 depletion step or batch (e.g. 3 days in the current work).
